Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Simplify language in the "older-Rahel" story.

An older Rahel learns that the block language she used to talk with
the turtle is also used to write all the software running inside
her special book.  Rahel begins to write stories with different
kinds of new music functionality, which make the green book even more
exciting for her younger brother and the other younger kids just now
receiving them.

>>>>

An older Rahel learns that the block language she used to talk with
the turtle is also used to write all the software and stories running inside
her special book.  Rahel begins to write new stories with her own
music and dialog, which make the green book even more
exciting for her younger brother and the other younger kids just now
receiving them.
